---
title: 'STAT 7240: project'
author: "Kelly Lavertu"
date: "October 18, 2023"
output:
  pdf_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

### **Instructions**
1. You must submit both your **.Rmd** and "knitted" **.pdf** (or **.html**) files to the appropriate Assignments Dropbox folder on D2L.<br />
2. This assignment is due **before class** on the due date listed above.<br />
3. You are allowed to work together on this assignment. List any classmates you collaborated with here (leave as is if you worked on it by yourself): **[insert classmates]**

### **Data**
In this assignment, you will be working with the following datasets:

  * *wine_testing.csv* - uploaded on D2L Assignment
  * *heart_train.csv* - uploaded on D2L Assignment 
  * *heart_test.csv* - uploaded on D2L Assignment 
  

```{r initiatePackages, message=FALSE}
# Packages: you can add/change (these are suggestions)
library(SciServer)
library(DBI)
library(dplyr)
library(dbplyr)
library(odbc)
library(imager)
library(httr)
library(jpeg)

library(tidyverse)
library(factoextra)
library(cluster)
library(tidyr)
library(ggplot2)
library(ggdendro)
library(dendextend)

```


```{r}
username = "kellylavertu"
password = "iDXPvvY!tkRJRf9"

auth_login = Authentication.login(username, password)

SkyServer.objectSearch(objId=NULL, specObjId=NULL, apogee_id=NULL, apstar_id=NULL, ra=NULL, dec=NULL, plate=NULL, mjd=NULL, fiber=NULL, run=NULL, rerun=NULL, camcol=NULL, field=NULL, obj=NULL, dataRelease=NULL)

# galaxy_query = "SELECT TOP 1000 p.objId,p.ra,p.dec,p.petror90_r, p.expAB_r,
#     p.dered_u as u, p.dered_g as g, p.dered_r as r, p.dered_i as i, 
#     s.z, s.plate, s.mjd, s.fiberid, g.p_cw as cw_spiral, g.p_acw as acw_spiral, g.p_edge as edgeon_spiral, g.spiral as spflag, g.elliptical as elflag, g.uncertain as ucflag
# FROM galaxy AS p
#    JOIN SpecObj AS s ON s.bestobjid = p.objid
#    JOIN zooSpec AS g ON g.objid = p.objid
# WHERE p.petror90_r > 10
#   and p.ra between 100 and 250
#   and s.z between 0.02 and 0.5
#   and p.g < 17"
# 
# galaxy_search = SkyServer.sqlSearch(sql = galaxy_query)
# galaxy_search
# print("Number of galaxies:")
# nrow(galaxy_search)
```




```{r}
# star_query = "SELECT TOP 10000 p.objId,p.ra,p.dec,p.petror90_r, p.expAB_r,
#     p.dered_u as u, p.dered_g as g, p.dered_r as r, p.dered_i as i, 
#     s.z, s.plate, s.mjd, s.fiberid
# FROM star AS p
#    JOIN SpecObj AS s ON s.bestobjid = p.objid"
# 
# star_search = SkyServer.sqlSearch(sql = star_query)
# star_search
# print("Number of stars:")
# nrow(star_search)
```


```{r}
# gal_plot = ggplot(data = galaxy_search) + geom_point(aes(x = galaxy_search$ra, y = galaxy_search$dec), fill = "black", size= 0.01) +
#   labs(
#     title = "GALAXY POSITIONS",
#     x = "RA",
#     y = "Dec")
# 
# plot(gal_plot)
```



```{r}
# star_plot = ggplot(data = star_search) + geom_point(aes(x = star_search$ra, y = star_search$dec), fill = "black", size= 0.01) +
#   labs(
#     title = "STAR POSITIONS",
#     x = "RA",
#     y = "Dec")
# 
# plot(star_plot)
```



```{r}
gal_sample_query = "SELECT TOP 1500 p.objId,p.ra,p.dec,p.petror90_r, p.expAB_r,
    p.dered_u as u, p.dered_g as g, p.dered_r as r, p.dered_i as i, 
    s.z, s.plate, s.mjd, s.fiberid, g.p_cw as cw_spiral, g.p_acw as acw_spiral, g.p_edge as edgeon_spiral, g.spiral as spflag, g.elliptical as elflag, g.uncertain as ucflag
FROM galaxy AS p 
   JOIN SpecObj AS s ON s.bestobjid = p.objid
   JOIN zooSpec AS g ON g.objid = p.objid
WHERE p.petror90_r > 10
  and p.ra between 100 and 250
  and s.z between 0.02 and 0.5
  and p.g < 17"
gal_sample_search = SkyServer.sqlSearch(sql = gal_sample_query)
gal_counter = 0
galaxy_type = ""
spiral_type = ""

# Function to download images
download_sdss_images <- function(objID, ra, dec, e, s, u, cw, acw, eo) {
  base_url <- "http://skyserver.sdss.org/dr16/SkyServerWS/ImgCutout/getjpeg"
  width <- 175
  height <- 175
  scale <- 0.1
  
  # Construct the download URL
  download_url <- paste0(base_url, "?TaskName=Skyserver.ObjectExplorer.GetJpeg",
                         "&ra=", ra,
                         "&dec=", dec,
                         "&width=", width,
                         "&height=", height,
                         "&scale=", scale)
  
  # Send GET request and download the image
  response <- GET(download_url)
  filename = ""
  # Check if the request was successful
  if (http_type(response) == "image/jpeg") {
    # Get raw content and write it to a binary file
    gal_counter <<- gal_counter + 1
    img_content = content(response, "raw")
    if(e == 1){
      galaxy_type = "elliptical"
      filename = file.path("C:/Users/Kelly/Documents/appdatamining/projectimages/galaxy", paste0("galaxy", gal_counter, "_", galaxy_type , ".jpeg"))}
    else if(s == 1){
      galaxy_type = "spiral"
      if(cw>acw & cw>eo){
        spiral_type = "clockwise"}
      else if(acw>cw & acw>eo){
        spiral_type = "anticlockwise"}
      else if(eo>acw & eo>cw){
        spiral_type = "edgeon"}
      filename = file.path("C:/Users/Kelly/Documents/appdatamining/projectimages/galaxy", paste0("galaxy", gal_counter, "_", galaxy_type , "_", spiral_type , ".jpeg"))
    }
    else{
      galaxy_type = "unknown"
      filename = file.path("C:/Users/Kelly/Documents/appdatamining/projectimages/galaxy", paste0("galaxy", gal_counter, "_", galaxy_type , ".jpeg"))
    }
      
    
    writeBin(img_content, filename)
    cat("Downloaded:", filename, "\n")
    }
  else {
    cat("Failed to download image for objID:", objID, "\n")
  }
}


for (i in 1:nrow(gal_sample_search)) {
  # I don't think I actually need these. just kidding I do need these
  objID <- gal_sample_search[i, "objId"]
  ra <- gal_sample_search[i, "ra"]
  dec <- gal_sample_search[i, "dec"]
  
  elliptical <- gal_sample_search[i, "elflag"]
  spiral <- gal_sample_search[i, "spflag"]
  unknown <- gal_sample_search[i, "ucflag"]
  cw <- gal_sample_search[i, "cw_spiral"]
  acw <- gal_sample_search[i, "acw_spiral"]
  eo <- gal_sample_search[i, "edgeon_spiral"]
  download_sdss_images(objID, ra, dec, elliptical, spiral, unknown, cw, acw, eo)
}

```


```{r}
# Load required libraries


star_sample_query = "SELECT TOP 1500 p.specObjID,p.ra,p.dec, subClass
FROM SpecObj AS p
WHERE class = \"Star\""

star_sample_search = SkyServer.sqlSearch(sql = star_sample_query)
star_counter = 0

# Function to download images
download_star_images <- function(objID, ra, dec, subclass) {
  base_url <- "http://skyserver.sdss.org/dr16/SkyServerWS/ImgCutout/getjpeg"
  width <- 175
  height <- 175
  scale <- 0.1
  
  # Construct the download URL
  download_url <- paste0(base_url, "?TaskName=Skyserver.ObjectExplorer.GetJpeg",
                         "&ra=", ra,
                         "&dec=", dec,
                         "&width=", width,
                         "&height=", height,
                         "&scale=", scale)
  
  # Send GET request and download the image
  response <- GET(download_url)
  
  # Check if the request was successful
  if (http_type(response) == "image/jpeg") {
    # Get raw content and write it to a binary file
    star_counter <<- star_counter + 1
    img_content = content(response, "raw")
    filename = file.path("C:/Users/Kelly/Documents/appdatamining/projectimages/star", paste0("star", star_counter, "_", subclass, ".jpeg"))
    writeBin(img_content, filename)
    cat("Downloaded:", filename, "\n")
    
  } else {
    cat("Failed to download image for objID:", specObjId, "\n")
  }
}

for (i in 1:nrow(star_sample_search)) {
  objID <- star_sample_search[i, "specObjID"]
  ra <- star_sample_search[i, "ra"]
  dec <- star_sample_search[i, "dec"]
  subclass <- star_sample_search[i, "subClass"]
  download_star_images(objID, ra, dec, subclass)
}

```


```{r}
qso_sample_query = "SELECT TOP 1500 s.specObjID, s.ra, s.dec, s.subClass
FROM SpecObj as s
WHERE class = \"QSO\""
qso_sample_search = SkyServer.sqlSearch(sql = qso_sample_query)
qso_counter = 0

# Function to download images
download_qso_images <- function(objID, ra, dec, subclass) {
  base_url <- "http://skyserver.sdss.org/dr16/SkyServerWS/ImgCutout/getjpeg"
  width <- 175
  height <- 175
  scale <- 0.1
  
  # Construct the download URL
  download_url <- paste0(base_url, "?TaskName=Skyserver.ObjectExplorer.GetJpeg",
                         "&ra=", ra,
                         "&dec=", dec,
                         "&width=", width,
                         "&height=", height,
                         "&scale=", scale)
  
  # Send GET request and download the image
  response <- GET(download_url)
  filename = ""
  # Check if the request was successful
  if (http_type(response) == "image/jpeg") {
    # Get raw content and write it to a binary file
    qso_counter <<- qso_counter + 1
    img_content = content(response, "raw")
    filename = file.path("C:/Users/Kelly/Documents/appdatamining/projectimages/quasar", paste0("quasar", qso_counter,"_", subclass , ".jpeg"))
    writeBin(img_content, filename)
    cat("Downloaded:", filename, "\n")
    
    }
  else {
    cat("Failed to download image for objID:", objID, "\n")
  }
}


for (i in 1:nrow(qso_sample_search)) {
  # I don't think I actually need these. just kidding I do need these
  if(i==103) 
    next
  objID <- qso_sample_search[i, "specObjID"]
  ra <- qso_sample_search[i, "ra"]
  dec <- qso_sample_search[i, "dec"]
  subclass <- qso_sample_search[i, "subClass"]
  download_qso_images(objID, ra, dec, subclass)
}
```

